The function--sheaf dictionary for smooth commutative group schemes over finite fields

### 2014-08-11 dictionary.tex
Changes to \S 3 in progress.
I need to putt this aside for the day, so I’m committing what I’ve got
so far.

We will identify $\bQC(G)$ with its image under $B_G$
and say that a quasicharacter sheaf $\qcs{L} \in \QC(G)$ is \emph{bounded}
if it is isomorphic to some $B_G(\qcs{L}_0, \mu_0)$.
We will see in Corollary~\ref{cor:bounded-and-finite} that bounded quasicharacter sheaves are exactly quasicharacter sheaves with bounded Trace of Frobenius.\todo{Check this, later.}

@@

In order to show that $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ is injective we need to recall some facts about Weil sheaves.
%

Now, let $\qcs{L}$ and $\qcs{L}'$ be quasicharacter sheaves on $G$ with $\trFrob{\qcs{L}} = \trFrob{\qcs{L}'}$.\todo{The rest of the proof is under construction.}
\end{proof}

@@

Recall from Section~\ref{sec:finite} that
a morphism $f : H\to G$ of group $\Fq$-schemes is a discrete isogeny
if it is a finite, surjective \'etale morphism and
the action of $\Gal(\bFq/\Fq)$ on the \'etale group scheme $\ker f$ is trivial.

@@

\begin{proposition}\label{prop:restriction}
For every quasicharacter sheaf $\qcs{L}^0$ on $G^0$ there is some finite quasicharacter sheaf
$\qcs{L}$ on $G$ such that $\qcs{L}\vert_{G^0} \iso \qcs{L}^0$.
As a consequence, the restriction functor $\iota_0^* : \QC(G)\to \QC(G^0)$ is essentially surjective.
\end{proposition}

>>>>

We will identify $\bQC(G)$ with its image under $B_G$
and say that a quasicharacter sheaf $\qcs{L} \in \QC(G)$ \emph{descends to a bounded quasicharacter sheaf} on $G$
if it is isomorphic to some $B_G(\qcs{L}_0, \mu_0)$.
We will see in Corollary~\ref{cor:bounded-and-finite} that bounded quasicharacter sheaves are exactly quasicharacter sheaves with bounded Trace of Frobenius.\todo{Check this, later.}

@@

Now, let $\qcs{L}$ and $\qcs{L}'$ be quasicharacter sheaves on $G$ with $\trFrob{\qcs{L}} = \trFrob{\qcs{L}'}$. We will show $\qcs{L} \iso \qcs{L}$.
We have just seen that $\qcs{L}$ and $\qcs{L}'$ descend to bounded quasicharacter sheaves on $G$: $B_G(\qcs{L}_0,\mu_0) \iso \qcs{L}$ and $B_G(\qcs{L}'_0,\mu'_0) \iso \qcs{L}'$.
Since bounded quasicharacter sheaves enjoy property \cite{laumon:87a}*{1.1.3.3}, \todo{Justify} it follows (arguing as in \cite{laumon:87a}*{1.1.2.1}) that there is an isomorphism $\qcs{L}_0 \to \qcs{L}'_0$. This morphism is compatible with $\mu_0$ and $\mu'_0$, \todo{Justify} hence a morphism of bounded quasicharacter sheaves.
Its image under $B_G$ is the isomorphism $\qcs{L} \to \qcs{L}'$ of quasicharacter sheaves we seek.
\end{proof}

@@

We say that a morphism $f : H\to G$ of commutative group $\Fq$-schemes is a discrete isogeny if it is a finite, surjective \'etale morphism and
the action of $\Gal(\bFq/\Fq)$ on the \'etale group scheme $\ker f$ is trivial.

@@

\begin{proposition}\label{prop:restriction}
%For every quasicharacter sheaf $\qcs{L}^0$ on $G^0$ there is some finite quasicharacter sheaf
%$\qcs{L}$ on $G$ such that $\qcs{L}\vert_{G^0} \iso \qcs{L}^0$.
%As a consequence, t
The restriction functor $\iota_0^* : \QC(G)\to \QC(G^0)$ is essentially surjective.
\end{proposition}
